EuPPollNet: A European database of plant-pollinator networks

### 2024-10-02 Manuscript/EuPPollNet_Ms.qmd
minor edits

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="90%", fig.width=12, fig.height= 8, fig.cap="\\textbf{Figure S6}. Distribution of z-scores comparing the nestedness of empirical networks with their randomized counterparts with a probabilistic null model from Bascompte et al., 2003 (100 null models for each network). This is the less restrictive approach, as it does not constrain the realised species degree. It first calculates the probability for each cell, and then if a random number between 0 and 1 exceeds this probability, an observed interaction is assigned to the cell. This shows that when the realised degree is not constrained, the number of networks that are statistically more nested is notably higher, highlighting that the nested structure is likely a byproduct of the species degree distribution."}

>>>>

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="90%", fig.width=12, fig.height= 8, fig.cap="\\textbf{Figure S6}. Distribution of z-scores comparing the nestedness (NODF) of empirical networks with their randomized counterparts with the probabilistic null model from Bascompte et al., 2003 (100 null models for each network). This is a less restrictive approach, as it does not completely constrain the realized species degree distributions. In a nutshell, the null model first calculates the probability of interaction for each cell, and then if a random number between 0 and 1 exceeds this probability, an observed interaction is assigned to the cell. This shows that when the realised degree is not fully constrained, the number of networks that are statistically more nested is notably higher, highlighting that the nested structure is likely a byproduct of the species degree distribution."}
